Case study validations of automatic bullet matching

### 2018-11-05 index.Rmd
eer

```{r aucs-pic, fig.cap=""}
aucs <- all_lands %>% gather(measure, score, rfscore, ccf, cms) %>% 
  group_by(study, group1, measure) %>% nest() %>%
  mutate(
    auc = data %>% purrr::map_dbl(function(d) {
      auc(d$sameland, d$score)
    }),
    auc_ci_low = data %>% purrr::map_dbl(function(d) {
      ci.auc(d$sameland, d$score)[1]
    }),
    auc_ci_high = data %>% purrr::map_dbl(function(d) {
      ci.auc(d$sameland, d$score)[3]
    })
  ) %>% 
  mutate(
    studyg = paste(study, group1) %>% str_trim %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3")),
    measure = factor(measure, levels = c("cms", "ccf", "rfscore"), labels = c("CMS", "CC", "RF")),
    measurenum = as.numeric(measure),
    measurechar = as.character(measure)
  )

@@

>>>>

```{r aucs-pic, fig.cap=""}
eer <- function(roc){
  dframe <- data.frame(sens = roc$sensitivities, 
                       spec = roc$specificities,
                       threshold = roc$thresholds)
  dframe$err1 <- 1 - dframe$sens
  dframe$err2 <- 1 - dframe$spec
  dframe$diff <- abs(dframe$err1-dframe$err2)
  dframe$eer <- (dframe$err1+dframe$err2)/2
  idx <- which.min(dframe$diff)
  dframe[idx,c("eer", "threshold")]
}

aucs <- all_lands %>% gather(measure, score, rfscore, ccf, cms) %>% 
  group_by(study, group1, measure) %>% nest() %>%
  mutate(
    auc = data %>% purrr::map_dbl(function(d) {
      auc(d$sameland, d$score)
    }),
    auc_ci_low = data %>% purrr::map_dbl(function(d) {
      ci.auc(d$sameland, d$score)[1]
    }),
    auc_ci_high = data %>% purrr::map_dbl(function(d) {
      ci.auc(d$sameland, d$score)[3]
    }),
    roc = data %>% purrr::map(function(d) {
      roc(d$sameland, d$score)
    }),
    errors = roc %>% purrr::map(.f = eer)
  ) %>% 
  mutate(
    studyg = paste(study, group1) %>% str_trim %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3")),
    measure = factor(measure, levels = c("cms", "ccf", "rfscore"), labels = c("CMS", "CC", "RF")),
    measurenum = as.numeric(measure),
    measurechar = as.character(measure)
  )
aucs <- aucs %>% unnest(errors)

@@

\hh{\autoref{fig:eer} shows an overview of Equal Error Rates (EER) based on the ROC curves of figure \ref{fig:roc-auc}. EERs are error rates when sensitivity and specificity of a test are equal, i.e. we see the same error rates of missing an identification for a land-to-land comparison  and wrong identifications, when it is determined that two land engraved areas come from the same source when they are, in fact, known to be from a different source. Equal error rates based on CMS of two lands are significantly higher than equal error rates based on cross-correlation or the RF score. At best, RF score and cross-correlation have an equal error rate of around 5\% for land-to-land comparisons. 
Interestingly, for consecutively matching striae, an equal error rate is reached for just two matching striae, which from a practical point of view is not sustainable. A  CMS of  6 or above is an established cutoff used in identifications. This leads to 0 wrong identifications but only identifies 21 out of  715 known same-source lands. XXX check after file names are corrected. }
```{r eval=FALSE}
xtabs(~sameland+I(cms>=12), data = all_lands)
```

```{r eer, fig.cap="Equal Error Rates for all measures (RF score, Cross-correlation and CMS) under all five (sub-)studies. CMS is signifcantly worse than both Cross-correlation and the RF score. At best, Cross-correlation and RF score have errors for land-to-land comparison of around 5%.", out.width = '.5\\textwidth'}
aucs %>% ggplot(aes(y = studyg, x = eer, colour=measure, shape = measure)) + 
  geom_point(size = 3) +theme_bw() +
  xlim(c(0, .35)) +
  xlab("Equal Error Rates (EER)") +
  ylab("") +
  scale_color_brewer(palette = "Set2")
```
